% LaTeX resume using res.cls
\documentclass[margin]{res}
% \usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\setlength{\textwidth}{5.1in} % set width of text portion

\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\begin{document}

\moveleft.5\hoffset\centerline{\LARGE\bf Florian Eckerstorfer}

% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{Sobieskigasse 12, A-1090 Vienna}
 \moveleft.5\hoffset\centerline{Phone +43 699 197 114 53 \quad Email florian@eckerstorfer.co}
 \moveleft.5\hoffset\centerline{Web \url{https://florian.ec}}


\begin{resume}

\section{EDUCATION}

\textbf{Master of Science,} Software Engineering and Internet Computing \\
	Vienna University of Technology, Vienna, AT, since October 2011

\textbf{Curriculum Supplement,} Innovation \\
	Vienna University of Technology, Vienna, AT, December 2013

\textbf{Bachelor of Science,} Software \& Information Engineering \\
	Vienna University of Technology, Vienna, AT, September 2011

\textbf{Graduation Diploma,} \emph{HLW für Kommunikations- und Mediendesign} (specialization in communications- and media design) \\
	\emph{Schulzentrum der Kreuzschwestern}, Linz, AT, June 2006


\section{EXPERIENCE}
\textbf{Frontend Developer} \hfill Since April 2016 \\
	Kiweno GmbH, Vienna, AT

\textbf{Web Developer} \hfill June 2009 - March 2016 \\
	2bePUBLISHED Internet Services Austria GmbH, Vienna, AT
	\begin{itemize}  \itemsep -2pt %reduce space between items
		\item Frontend Development (HTML, CSS, JavaScript, AngularJS)
		\item Web Development with PHP and Symfony
		\item Web Data Extraction and Business Intelligence
	\end{itemize}

\textbf{Web Developer} \hfill August 2008 - May 2009 \\
	2beFOUND Performance Marketing GmbH, Vienna, AT
	\begin{itemize}  \itemsep -2pt
		\item Frontend Development (HTML, CSS, JavaScript)
		\item Web Development with PHP and Symfony
	\end{itemize}

\textbf{Freelancer} \hfill January 2002 - May 2009 \\
	Various client work
	\begin{itemize}  \itemsep -2pt
		\item Frontend Development
		\item Web Development
		\item Web Design
		\item Consulting
	\end{itemize}

\textbf{Internship} \hfill August 2004 \\
	Strobl)Kriegner Group, Linz, AT
	\begin{itemize}  \itemsep -2pt
		\item Web Design
		\item Print Design
		\item Flash Development
	\end{itemize}

\textbf{Internship} \hfill August 2003, June - July 2004 \\
	CREATEAM Werbeagentur GmbH, Linz, AT
	\begin{itemize}  \itemsep -2pt
		\item Web Design
		\item Print Design
		\item Frontend Development
	\end{itemize}

\clearpage

\section{OPEN SOURCE \\ PROJECTS}

\textbf{BraincraftedBootstrapBundle} \\
	Bundle to easily integrate Twitter Bootstrap in a Symfony2 project. As of May 2014 about 90k downloads. \url{http://bootstrap.braincrafted.com}

\textbf{Slugify} \\
	Library to create URL slugs from strings with support for a wide range of languages. As of May 2014 over 20k downloads. \url{https://github.com/cocur/slugify}

\textbf{Symfony2 Forms Framework} \\
	Contributed with three other students to a framework to create, validate and submit forms. Part of the Symfony2 Framework. \url{http://symfony.com}

A full list of open source code I work is available on my Github profile: \url{https://github.com/florianeckerstorfer}.

\section{PRIVATE \\ PROJECTS}

\textbf{Similar.fm} \hfill March 2012 \\
	Web Service to easily open music related to the music a user is currently listening to in Spotify. \url{http://similar.fm}

\textbf{Tryp} \hfill August 2011 \\
	Web Service to visualize the previous whereabouts of a Twitter user on a map. \\ \url{http://trypapp.com} (No longer online)

\textbf{RegExp Tester} \hfill July 2010 \\
	Web Service to easily test regular expressions. \\ \url{http://regexptester.com} (No longer online)

\textbf{Ninjawhois} \hfill April 2009 \\
	Web Service to check the availability of multiple domains. \\ \url{http://ninjawhois.com} (No longer online)

I have been working on a wide variety of private projects since 1999. A comprehensive overview is presented at \url{https://florian.ec/projects}.


\section{LANGUAGES}

\textbf{German:} Mother tongue \\
\textbf{English:} Excellent reading (C2) and very good writing and speaking skills (C1) \\
\textbf{Spanish:} Basic reading, writing and speaking skills (A2)


\end{resume}

\vspace{15 mm}

The most recent version of my CV is available at \url{https://florian.ec/cv}.

A recent PDF version is available at \url{https://florian.ec/cv.pdf}.

\end{document}




